|

### 2025-07-09 output/IMPS-2025-slideshow.qmd
Add "assumptions" slide

That is why Reckase & McKinley propose to find a way of describing the characteristics of multidimensional items, taking their dimensionality into account.

They do it in this 1985 paper, and a subsequent one in 1991...
:::

@@

::: notes
...where they define the item discrimination, which can in turn be used to define the item difficulty.

Note that the difficulty has two components: a "signed distance" from the origin, and a direction.

@@

>>>>

That is why Reckase proposes to find a way of describing the characteristics of multidimensional items, taking their dimensionality into account.

He do it in this 1985 paper, and in a subsequent one in 1991...
:::

@@

::: notes
...Reckase & McKinley define the item discrimination, which is an extension of the Pythagorean theorem.

Note also that the discrimination can in turn be used to define the item difficulty, as happens in the unidimensional model.

And also, that the difficulty has two components: a "signed distance" from the origin, and a direction.

@@

## Assumptions {.smaller}

@reckase_difficulty_1985:

-   Increasing monotony:

---(p. 402)

-   Orthogonality

---(p. 404)

::: notes
However, there are two assumptions that Reckase & McKinley make when obtaining the definition of the multidimensional parameters.

The first is that the probability of answering an item correctly always increases monotonically with respect to each dimension.

The second, that constrain that you see there, implies that the item is represented in an orthogonal basis.
That is the reason why the discrimination is defined by a "general Pythagorean theorem".
:::
